Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-15 writing/DraftExposurePaper/DraftExposurePaper.Rmd
try to update draft
table with literature and parameters

```{r}
library(hurricaneexposure)
```

@@

Currently, it seems that most hurricane track mapping capabilities are restricted to geographical information system software. The introduction of this package expands the mapping potential of hurricane tracks and therefore the assessment of hurricane exposure and impacts to R.

@@

@@

References {#references .unnumbered}
==========

>>>>

```{r}
library(hurricaneexposure)
library(knitr)
```

@@

Currently, it seems that most hurricane track mapping capabilities are restricted to geographical information system software. The introduction of this package expands the mapping potential of hurricane tracks, and therefore the assessment of hurricane exposure and impacts, to R.

@@

Most distance exposure definitions in the past have been based on maximum wind radii based on maximum sustained winds [@Kruck2010].

@@

#### Table including various exposure papers and the parameters used

```{r}
studies <- c("Czajkowski 2010", "Rezempour 2014", "Zandbergen 2009", 
             "Currie 2013", "Grabich 2016", "Zaharan 2010", "Kruck 2010", 
             "Villarini 2011", "Atallah 2007")
distance_km <- c("120", "", "Buffer", "25, 30, 60, 75", "30, 60, 100", 
                 "2 counties", "Radial Max Wind", "100-500", "")
rain_mm <- c("", "2/hr, 48/d", "", "", "", "", "", "", "200-500 (Floyd)")
wind_kt <- c("", "", "SSWS", "", "SSWS", "", "34, 50, 64", "", "")
exposure_parameters <- data.frame(studies, distance_km, rain_mm, wind_kt)
kable(exposure_parameters, "markdown")
```
SSWS = Staffir-Simpson Hurricane Wind Scale (TS, 1, 2, 3, 4, and 5). Wind Cutoffs at 34, 64, 83, 96, 113, and 137 kt.  
References {#references .unnumbered}
==========
